Word-Level Abstractions for Sequential Design Verification using Algebraic Geometry

### 2016-12-15 dissertation/slides/defense.tex
dissertation: defense slides v2

@@

\begin{frame}{\large{Preliminaries: Buchberger's algorithm computes a Gr\"obner basis}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%(End of copy)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Improve complexity using RATO [Pruss, '15]}}

@@

\item Directly compute GB($J_{ckt}+J_0$) in $\Fq$ is costly ($q^{O(d)}$)
\item GB sensitive to term order$\to$Transform to simpler set for GB?

@@

\item RATO: reverse topological traverse on ckt structure

@@

\includegraphics[width=4.5in]{../newfig/new_stg.eps}
\label{fig:fsm}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Benefits of using RATO}}

@@

\item Definition of RATO:\par 
``bit-level variables ordered reverse topologically "$ > T>S$
\item Only one pair of poly with non-relatively-prime leading terms

@@

	\item If $gcd(lt(f_w),lt(f_g)) = 1$:
	\item $Spoly(f_w,f_g) \xrightarrow{J_{ckt}+J_0}_+ 0$

@@

\item Topology in structure

@@

	\item Each poly with leading term -- fanout
	\item Divide with levelization
	\item Only inputs (primary \& pseudo) left!

@@

\begin{frame}{\large{Example of using RATO}}

@@

\item RATO: LEX with $(t_0,t_1)>(a,b,c,d)>(x,s_0,s_1)>T>S$
\begin{equation*}
f_1: a+xs_0s_1+xs_0+xs_1+x+s_0s_1+s_0+s_1+1
\end{equation*}
\vspace{-0.8cm}
\begin{alignat*}{2}
f_2: b+s_0s_1 &~~~ f_3: c+x+xs_0 &&~~~f_4: d+s_0s_1+s_0 \\

>>>>

\hyperlink{expSMPO}{\beamergotobutton{Go back to Exp result}}

@@

\begin{frame}[label = Buch]{\large{Preliminaries: Buchberger's algorithm computes a Gr\"obner basis}}

@@

\hyperlink{linkRATO}{\beamergotobutton{RATO}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%(End of copy)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Improve complexity using RATO [Pruss, '15]}}
\bi
\item Directly compute GB($J_{ckt}+J_0$) in $\Fq$ is costly ($q^{O(n)}$)
\item GB sensitive to term order$\to$Transform to simpler set for GB?
\pause
\item RATO: reverse topological traverse on ckt structure
\ei
\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{../newfig/new_stg.eps}
\label{fig:fsm}}
\end{figure}
\hyperlink{Buch}{\beamergotobutton{Buchberger}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = linkRATO]{\large{Benefits of using RATO}}
\bi
\item Definition of RATO:\par 
``bit-level variables ordered reverse topologically "$ > T>S$
\item Topology in ckt structure
	\bi
	\item Output of each gate $= lt(f_i)$
	\ei
\item Product criterion: $gcd(lt(f_i),lt(f_j)) = 1 \implies Spoly(f_i,f_j) \xrightarrow{J_{ckt}+J_0}_+ 0$
\item Only one pair of poly with non-relatively-prime leading terms

\item $Spoly$ division
	\bi
	\item Divide with levelization
	\item Only inputs (primary \& pseudo) left!
	\ei
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Example of using RATO}}
\bi
\item RATO: LEX with $(t_0,t_1)>(a,b,c,d)>(x,s_0,s_1)>T>S$
\ei
\begin{equation*}
f_1: a+xs_0s_1+xs_0+xs_1+x+s_0s_1+s_0+s_1+1
\end{equation*}
\vspace{-0.8cm}
\begin{alignat*}{2}
f_2: b+s_0s_1 &~~~ f_3: c+x+xs_0 &&~~~f_4: d+s_0s_1+s_0 \\
f_5: \alert{t_0}+ab+a+1 &~~~ f_6: t_1+cd+c+d &&~~~ f_7: \alert{t_0}+t_1\alpha+T 
\end{alignat*}
\bi
\item $Spoly$ reduction gives $T+\Func(primary/pseudo~inputs)$
\ei
\begin{align}
&Spoly(f_5,f_7) \xrightarrow{J_{ckt}+J_0}_{+}T + s_0 s_1 x+\alpha s_0 s_1 \nonumber\\
&+(1+\alpha)s_0 x+(1+\alpha) s_0+s_1 x+s_1+(1+\alpha) x+1\nonumber
\end{align}
\bi
\item {\bf Q:} How to get rid of bit-level inputs?
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Bit-to-word conversion}}
\bi
\item Objective: find $s_i = \mathcal G(S)$
\item $(s_0+s_1\alpha+\cdots+s_{k-1}\alpha^{k-1})^{2^n} = s_0^{2^n}+(s_1\alpha)^{2^n}+\cdots+(s_{k-1}\alpha^{k-1})^{2^n}$
\item Build system of poly eqns by squaring:
\begin{align*}
\label{eqn:alphamat}
\begin{bmatrix}
S \\
S^2 \\
S^{2^2} \\
\vdots \\
S^{2^{k-1}}
\end{bmatrix}
&=
\begin{bmatrix}
1 & \alpha & \alpha^{2} & \cdots & \alpha^{{k-1}}\\
1 & \alpha^{2} & \alpha^{4} & \cdots & \alpha^{2(k-1)} \\
1 & \alpha^{4} & \alpha^{8} & \cdots & \alpha^{4(k-1)}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \alpha^{2^{k-1}} & \alpha^{2\cdot 2^{k-1}} & \cdots & \alpha^{(k-1)\cdot 2^{k-1}}
\end{bmatrix}
\begin{bmatrix}
s_0\\
s_1\\
s_2\\
\vdots\\
s_{k-1}
\end{bmatrix}
\end{align*}
\item Transition function $f_T: T+\Func(S,x)$
\item Elimination on ideal $\langle f_T,f_S \rangle+J_0$ using $S,x > T$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{FSM traversal algorithm with RATO}}
\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\LinesNumbered
\Indm
 \KwIn{Polynomial ideal $J_{ckt}$, initial state polynomial $\Func(S)$}
 \KwOut{Final reachable states represented by polynomial $\mathcal G(T)$}
\Indp

  $from^0 = reached = \Func(S)$\;
  $f_T = $Reduce($Spoly(f_w,f_g), J_{ckt})$\;
  \tcc{Compute $Spoly$ for the critical pair, then reduce it with circuit ideal under RATO}
	Eliminate bit-level variables in $f_T$\;
  \Repeat{$\langle new^i\rangle == \langle 1\rangle$}
  {
  	$i \gets i + 1$\;
  	$G \gets$GB($\langle f_T , from^{i-1}\rangle+J_0^{PI}$)\;
%  	\tcc{Compute Gr\"obner basis with elimination term order: $T$ smallest; $J_0^{PI}$ covers all possible inputs from PIs}
	$to^i \gets G\cup \Fkk[T]$\;
%	\tcc{There will be a univariate polynomial in $G$ denoting next state in word-level variable $T$}
	$\langle new^i\rangle \gets \langle to^i\rangle + (\langle T^{2^k}-T\rangle:\langle reached\rangle)$\;
%	\tcc{Use quotient of ideals to attain complement of reached states, then use sum of ideals to attain an intersection with next state}
  	$\langle reached\rangle \gets \langle reached\rangle \cdot \langle new^i\rangle$\;
%  	\tcc{Use product of ideals to attain a union of new reached states and formerly reached states}
	$from^i \gets new^i(S\setminus T)$\;
%	\tcc{Start a new iteration by replacing variable $T$ in new reached states with current state variable $S$}
  }
%  \tcc{Loop until a fix-point reached: newly reached state is empty}
\Return{$\langle reached\rangle$}
\caption {Refined Algebraic Geometry based FSM Traversal}\label{alg:refined}
\end{algorithm}
\DecMargin{1em}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Experiment results: word-level traversal}}
\begin{table}[H]
\centering
\caption{Results of running benchmarks using our tool. 
\small{Parts I to III denote the time taken by polynomial divisions,
  bit-level to word-level abstraction and iterative reachability
  convergence checking part of our approach, respectively.}}
{\small 
\begin{tabular}{|c||c|c|c|c|c|c|}
\hline
\multirow{3}{*}{\centering Benchmark} 
 & \multirow{3}{0.9cm}{\centering \# States}
 & \multirow{3}{1.3cm}{\centering \# iterations}
 & \multicolumn{3}{c|}{\multirow{2}{2.0cm}{\centering Runtime (sec)}}
 & \multirow{3}{1.8cm}{\centering Runtime of VIS (sec)} \\
   & & &\multicolumn{3}{c|}{}& \\
  \cline{4-6}
     & & & I & II & III & \\
\hline
\hline
b01 & 18  & 5  & $<0.01$ & 0.01 & 0.02 & $<0.01$\\
b02 & 8 & 5 & $<0.01$  & 0.01 & $<0.01$ & $<0.01$ \\
b06 & 13 & 4 & $<0.01$ & 0.07 & 5.0 & $<0.01$ \\
s27 & 6 & 2 & $<0.01$ & 0.01 & 0.02  & $<0.01$  \\
s208 & 16 & 16 & $<0.01$ & 0.32 & 2.4 & $<0.01$ \\
s386 & 13  & 3 & 1.0 & 7.6 & 8.2  & $<0.01$ \\
bbara & 10 & 6 & 0.04 & 0.01 & 0.04  & $<0.01$ \\
beecount & 7  & 3  &$<0.01$ & 0.01 & 0.01 & $<0.01$ \\
dk14 & 7  & 2  & 45 & $<0.01$ & 0.08 & $<0.01$\\
donfile & 24 & 3  & 12316 & 0.02 & 1.7  & $<0.01$\\
\hline
\end{tabular}
}
\label{tab:result}  
\end{table} 
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = Moore]{\large{Apply FSM traversal to arithmetic ckts}}
\vspace{-0.1in}
\begin{figure}[hbt]
\centering{
%\begin{minipage}{12cm}
\includegraphics[width=4.5in]{../newfig/Moore.eps}
% \vspace{-0.2in}
%\caption{A simple Moore FSM and its state transition graph}
%\end{minipage}
\label{fig:Moore}}
\end{figure}
\vspace{-0.4in}
\bi
\item Model: restricted Moore finite state machine
	\bi
	\item Some sequential arithmetic circuits will give results after running for $k$ clock cycles
	\item The initial operands are preloaded in register files
	\ei
\item State transitions on this model:
$$R_{k} = Tr(R_{k-1}) = Tr(Tr(\cdots Tr(R_{init})\cdots)) = Tr^k(R_{init})$$
\item Word-level unrolling
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall unrolling}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Galois field multiplier}}
SPEC: $R = A_{init}\cdot B_{init} \pmod {P(\alpha)}$ after $k$ clock cycles
\hspace{-0.3in}\begin{figure}[hbt]
\centering{
%\begin{minipage}{12cm}
\includegraphics[width=5in]{./new_multi.eps}
%\end{minipage}
\label{fig:RHmulti}}
\end{figure}
\bi
\item Projection on NS $R',A',B'$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{GF multiplier verification algorithm}}
\begin{algorithm}[H] % note [hbt] will fail in beamer
\SetAlgoNoLine
 \KwIn{Circuit polynomial ideal $J$, vanishing ideal $J_0$, initial state ideal $R (=0), \mathcal{G}(A_{init}), \mathcal{H}(B_{init})$}

  $from_0(R,A,B) = \langle R, \mathcal{G}(A_{init}), \mathcal{H}(B_{init})\rangle$\;
  $i = 0$\;
  \Repeat{$i == k$}
  {
  	$i \gets i + 1$\;
	\alert{$f_o \xrightarrow{J + J_0+ from_{i-1}(R,A,B)}_+ f_r$ under RATO} \;
	\alert{$to_i(R',A',B')\gets f_r(\{R',A',B'\}\setminus\{r_0,\dots,r_{k-1},a_0,\dots,a_{k-1},b_0,\dots,b_{k-1}\}$}\;
	$from_i \gets to_i(\{R,A,B\}\setminus \{R',A',B'\})$\;
  }
\Return{$from_k(R_{final})$}
\caption {Abstraction via implicit unrolling for Sequential GF circuit verification}
\end{algorithm}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = expSMPO]{\large{Experiment result: sequential GF multiplier verification}}
\bi
\item Run-time for verification of bug-free RH-SMPO circuits
  for SAT, ABC and BDD based methods. \emph{TO} = timeout 14 hrs
\begin{table}[H]
\centering
\label{tbl:equiv}
\begin{tabular}{|c||c|c|c|c|} 
\hline
& \multicolumn{4}{|c|}{Word size of the operands $k$-bits}  \\
\hline
Solver & 11 & 18 & 23 & 33 \\
\hline
\hline
Lingeling & 593  & \emph{TO}  & \emph{TO}  & \emph{TO}\\
\hline
\hline
ABC & 6.24 & \emph{TO} & \emph{TO} & \emph{TO}\\
\hline
\hline
BDD & 0.1 & 11.7 & 1002.4 & \emph{TO}  \\
\hline
\end{tabular}
\label{table:satbdd}  
\end{table} 
\item Runtime for verification of bug-free Agnew's and RH-SMPO circuits using our approach
\hspace{-0.3in}\begin{table}[H]
\centering
\label{tab:Cpp}
{\small 
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c||}{\centering Operand size $k$} & 36 & 60 & 81 & 100 & 131 & 162 \\
\hline
\multirow{2}{1cm}{\centering RH-SMPO} & \#Polys & 4716 & 12960 & 21870 & 35600 & 56592 & 92826 \\
\cline{2-8}
 & Runtime & 14.3 & 213.3 & 1343 & 4685 & 26314 & 124194 \\
\hline
\multirow{2}{1cm}{\centering Agnew's SMPO} & \#Polys & 2700 & 7380 & 13356 & 20300 & 34715 & 52974 \\
\cline{2-8}
 & Runtime & 10.2 & 212.0 & 2684 & 4686 & 56568 & 119441 \\

\end{tabular}
}
\end{table}
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall SEC miter}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{UNSAT problems: refutation within Buchberger's algorithm}}
\begin{Theorem}[Weak Nullstellensatz]
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_n]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_n] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
\bi
\item Recall Buchberger's algorithm: UNSAT $\to$ terminates with $1$
\pause
\item  Information lies in $Spoly$?
\item Poly calculus stronger than resolution!
\ei

\begin{Definition}
Assume a polynomial set $F$ is UNSAT. A subset $M \subseteq F$ is an {\bf UNSAT core} 
if $M$ is also UNSAT. Further, if $\forall f\in M$, $M\setminus\{f\}$ is SAT, then 
$M$ is called a {\bf minimal UNSAT core} of $F$.
\end{Definition}

Animation 2...
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Motivating example}}
\bi
\item $f_1\sim f_9 \in \mathbb{F}_2[a,b,c,d]$
\item $F = \{f_1,f_2,\dots,f_9\}$
\ei

\begin{minipage}{2in}
\begin{align*}
f_1&: abc + ab + ac + bc \\
   & + a + b + c + 1\\
f_2&: b\\
f_3&: ac\\
f_4&: ac + a
\end{align*}
\end{minipage}
%\hspace{0.1in}
\begin{minipage}{2in}
\begin{align*}
f_5&: bc + c\\
f_6&: abd + ad + bd + d\\
f_7&: cd\\
f_8&: abd + ab + ad + bd + a + b + d + 1\\
f_9&: abd + ab +bd + b
\end{align*}
\end{minipage}
\vspace{1cm}
\bi
\item Find a subset $F_c \subset F$ {\it s.t.} $F_c$ remains UNSAT 
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Motivating example}}
Following Spoly selection strategy $(f_1,f_2)\to (f_1,f_3) \to (f_2,f_3)\to (f_1,f_4) \to \cdots$,
execute Buchberger's algorithm until adding ``1" to Gr\"obner basis
\bi
\item $Spoly(f_1,f_2)= f_1 - ac\cdot f_2\xrightarrow{a\cdot f_2} ~\xrightarrow{f_3}~
\xrightarrow{c\cdot f_2}  ~\xrightarrow{f_2} f_{10}=a+c+1$
\item $Spoly(f_1,f_3)\xrightarrow{F}_+ 0$
\item \dots
\item $Spoly(f_3,f_4)\xrightarrow{f_{10}} f_{11} = c+1$
\item $Spoly(f_2,f_5)\xrightarrow{f_{11}} 1$
\ei
$\{f_1,\dots,f_9,f_{10},f_{11},1\}$ is the Gr\"obner basis generated from Buchberger's algorithm
\end{frame}

\begin{frame}{\large{Motivating Example: Refutation Tree}}
\vspace{-0.1in}
\includegraphics[width=3.5in]{./refutation_1.pdf}
\pause
\bi
\item $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\item $1 = \F(f_1,f_2,f_3,f_4,f_5)\implies 1 \in \langle f_1,f_2,f_3,f_4,f_5\rangle \implies UNSAT$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size: redundancy in refutation tree}}
\bi
\item Expand: \begin{align*}
		1 &= \F(f_1,f_2,f_3,f_4,f_5)\\
		&= cf_2+f_5+\alert{f_{11}}\\
		&=cf_2+f_5+f_3+f_4+\alert{f_{10}}\\
		&=(cf_2 + f_5) + \dots + \mathbf{1\cdot f_3} + \dots + \mathbf{1\cdot
  f_3}+ \dots + (f_1 + acf_2)
		\end{align*}
\item UNSAT core reduced to $\{f_1,f_2,f_4,f_5\}$ which is {\bf minimal}
\item \alert{GB-core algorithm}:
	\bi
	\item Execute Buchberger's algorithm
	\item Recording data including Spoly, polynomials for division and remainder
	\item Terminate Buchberger's algorithm after recording remainder ``1"
	\item Build refutation tree and get UNSAT core
	\item Analyze recorded data, remove redundant polynomials from the core
	\ei
\ei
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size: iterative refinement}}
\bi
\item Spoly pair selection strategy: $(f_1,f_2)\to(f_1,f_3)\to(f_2,f_3)\to(f_1,f_4)\to(f_2,f_4)\to\cdots$
\item High likelihood in minimal core $\to$ Put ahead in Spoly queue $\to$ Faster approaching ``1" in GB-core $\to$ Smaller core
\ei
\vspace{-0.2in}
\begin{columns}[onlytextwidth]
\begin{column}{0.5\textwidth}
\begin{figure}
\centering
\includegraphics[scale=0.25]{refutation_2.pdf}
%\caption{Refutation distance \& frequency}
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\bi
\item {\bf Refutation distance}: shortest path to leaf
\item Distance$\downarrow \to$ LT Degree$\downarrow \to$ Likelihood in minimal core $\uparrow$
\vspace{0.2in}
\item {\bf Frequency}: number of times $f_i$ appears in refutation tree
\ei
\end{column}
\end{columns}
\end{frame}

\begin{frame}{\large{Iterative refinement Example}}
\vspace{-0.1in}
\begin{alignat*}{4}
& f_1: x_1x_3+x_3 && ~~~f_2: x_2 + 1 && ~~~f_3: x_2x_3+x_2 \\
& f_4: x_2x_3 && ~~~f_5: x_2x_3 + x_2 + x_3 + 1 && ~~~f_6 : x_1x_2x_3 +x_1x_3
\end{alignat*}
\vspace{-0.5in}
\begin{columns}[onlytextwidth]
\begin{column}{0.6\textwidth}
\begin{figure}
\centering
\includegraphics[scale=0.3]{iterative_1.pdf}
\end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\bi
\item $F=\{f_1,f_2,\dots,f_6\}\in\mathbb{F}_2[x_1,x_2,x_3]$
\item UNSAT core: $f_1,f_2,f_3,f_4$
\item \alert{Refutation distance}: \\
		$f_2~~f_1~~f_3~~f_4$\\
		$2~~~3~~~3~~~3$
\item \alert{Frequency}:\\
		$f_1~~f_3~~f_4$\\
		$1~~~1~~~1$
\item Reorder: $\alert{f_2},f_1,f_3,f_4$
\ei
\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Iterative refinement: iteration 2}}
\vspace{-0.1in}
\begin{alignat*}{4}
& f_1: x_1x_3+x_3 && ~~~f_2: x_2 + 1 && ~~~f_3: x_2x_3+x_2 \\
& f_4: x_2x_3 && ~~~f_5: x_2x_3 + x_2 + x_3 + 1 && ~~~f_6 : x_1x_2x_3 +x_1x_3
\end{alignat*}
\vspace{-0.5in}
\begin{columns}[onlytextwidth]
\begin{column}{0.6\textwidth}
\begin{figure}
\centering
\includegraphics[scale=0.3]{iterative_2.pdf}
\end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\bi
\item New order: $f_2,f_1,f_3,f_4$
\item Spoly pairs selection:\\
	$(\alert{f_2},f_1)\to(\alert{f_2},f_3)\to(f_1,f_3)\to(\alert{f_2},f_4)\to(f_1,f_4)\to(f_3,f_4)$
\item UNSAT core: $f_2,f_3,f_4$
\item \alert{Fixpoint reached}
\ei
\end{column}
\end{columns}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{\large{Reducing size further using syzygy heuristic}}
\bi
\item Finding interdependencies: $f_i\in\langle F\setminus\{f_i\}\rangle$?
\item Given $F=\{f_1,\dots,f_s\}$, find $f_i = \sum_{j\neq i} h_jf_j$
\item Info lost in refutation tree/Buchberger's algorithm?
\item Inner loop of Buchberger's algorithm: \\
\hspace{0.2in}  $Spoly(f, g) \stackrel{G'}{\textstyle\longrightarrow}_+
r$ \\
\hspace{0.2in}  \alert{IF $r \neq 0$} THEN $G:= G \cup \{r\}$ \\
\hspace{0.2in}  \alert{IF $r = 0$} THEN Discard

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size further using syzygy heuristic}}
\bi
\item In a single syzygy, $c_i=1 \implies f_i = \sum_{j\neq i} h_jf_j$
\item In general cases, need to analyze all syzygies recorded
\item Collect $m$ syzygies as a system of polynomial equations, or a {\bf Syzygy Matrix}
\ei
\hspace{-0.1in}
\begin{minipage}{2.5in}
\begin{equation*} \label{eqn:syz}
 \begin{cases}
 c_1^1f_1+c_2^1f_2+\cdots+c_s^1f_s = 0\\
 c_1^2f_1+c_2^2f_2+\cdots+c_s^2f_s  = 0\\
 \ \ \ \ \ \  \vdots \\
 c_1^mf_1+c_2^mf_2+\cdots+c_s^mf_s = 0  
 \end{cases}
\end{equation*}
\end{minipage}
\hspace{-0.3in}
\begin{minipage}{2in}
%which can be represented in matrix form as:
\begin{center}
\begin{align*}
\label{mat:syzygy}
   \begin{bmatrix}
           c_1^1 & c_2^1 & \cdots & c_s^1 \\
           c_1^2 & c_2^2 & \cdots & c_s^2 \\
           \vdots & \vdots & \ddots & \vdots \\
           c_1^m & c_2^m & \cdots & c_s^m
         \end{bmatrix}
    \begin{bmatrix}
           f_{1} \\
           f_{2} \\
           \vdots \\
           f_{s}
         \end{bmatrix}
         &= 0
  \end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size: revisiting motivating example with syzygy}}
\vspace{-0.2in}
\begin{columns}[onlytextwidth]
\begin{column}{0.5\textwidth}
\begin{figure}
\centering
\includegraphics[scale=0.25]{refutation_tree.pdf}
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\bi
\item Recorded in Buchberger's Algo:\\
$Spoly(f_1,f_2)\xrightarrow{F}_+ f_{10}$\\
$Spoly(f_3,f_4)\xrightarrow{F}_+ f_{11}$\\
$Spoly(f_2,f_5)\xrightarrow{F}_+ 1$
\item Discarded in Buchberger's Algo:\\
$Spoly(f_1,f_3)\xrightarrow{F}_+ 0$\\
$Spoly(f_2,f_3)\xrightarrow{F}_+ 0$\\
$\dots$\\
$Spoly(f_1,f_5)\xrightarrow{F}_+ 0$
\ei
\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: setup}}
\bi
\item Syzygy matrix:
\ei
\includegraphics[width=4.5in]{./syzygy_1.pdf}
\pause
\llap{\includegraphics[width=4.5in]{./syzygy_2.pdf}}
\bi
\item rows: syzygies
\item $J = \langle f_1,f_2,\dots,f_9\rangle$
\item $f_{10}\in J$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy Example: refine syzygy matrix}}
\bi
\item Considering $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\ei
\includegraphics[width=4.5in]{./syzygy_3.pdf}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: derive interdependency}}
\includegraphics[width=4.5in]{./syzygy_4.pdf}
\bi
\item Column $f_3$ contains ``1", means:\\
$1\cdot f_3 + ac f_2 + a f_5 = 0\Leftrightarrow f_3 = acf_2+af_5$
\item Generalization of this strategy refer to the paper
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Overall Approach}}
\begin{algorithm}[H] % note [hbt] will fail in beamer
\SetAlgoNoLine
 \KwIn{A set of UNSAT polynomials $F$} 
 \KwOut{A subset $F'\subset F$ remains UNSAT}
 $G \gets F$\;
  \Repeat{$G=F'$}
  {
	$F' = G$\;
  	$G \gets $GB-core($F'$ with order $>$)\;
	Update order $>$\;
  }
  $F'\gets$syzygy\_heuristic($G$)\;
\Return{$F'$}
\caption {UNSAT core extraction based on Gr\"obner basis algorithm}
\end{algorithm}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Application to abstraction refinement}}
\includegraphics[scale=0.35]{../newfig/s27.pdf}
\vspace{-0.3in}

@@

\item PS = $\{G7,G6,G5\}$, NS = $\{G13,G11,G10\}$: 8 states
\item Property $p = {\bf AG}( (\neg G13) {\bf U} (\neg Z) )$
\item $k$-BMC without abstraction refinement: when $k=3$ prove $PASS$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Application to abstraction refinement}}
\item Circuit ideal when $k=0$:
I = \langle & G14+1+G0, G8+G14\cdot G6, G15+G12+G8+G12\cdot G8,\\ 
	& G16+G3+G8+G3\cdot G8, G9+1+G16\cdot G15, \\ 
	& G10+1+G14+G11+G14\cdot G11, G11+1+G5+G9+G5\cdot G9, \\
	& G12+1+G1+G7+G1\cdot G7, G13+1+G2+G12+G2\cdot G12, \\
	& Z+1+G1, \\
	& \text{(Initial state 000 )} G5, G6, G7 \rangle;
\item Property: $\neg p = Z\cdot G13 + 1$
\item UNSAT core: \begin{align*}
Core(I\land \neg p) =& G12+1+G1+\alert{G7}+G1\cdot \alert{G7},\\
&\alert{G13}+1+G2+G12+G2\cdot G12, \\
& Z+1+G1, \alert{G7};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Application to abstraction refinement}}
\includegraphics[scale=0.25]{../newfig/s27_stg.pdf}
\includegraphics[scale=0.25]{../newfig/s27_stg_refined.pdf}
\item $\{G5/G10 ,G6/G11\}$: irrelevant
\item By removing irrelevant latches, state-space reduced
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Conclusion}}
\item Word-level abstraction of state-space
\item Apply to reachability analysis
\item Prove effectiveness by experiments on ISCAS'89 and ITC'99 benchmarks

@@

\item Word-level abstraction of function in a single time-frame
\item Apply to functional correctness checking of sequential GF multipliers
\item Succeed to verify 162-bit, while contemporary fails beyond 23 bit 

@@

\item UNSAT core extraction for a set of polynomials
\item Refine the core using refutation proof \& syzygies
\item UNSAT core info can be applied to abstraction refinement

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Future work}}

@@

\item Multivariate polynomial ideals

@@

	\item Extend the application of univariate polynomial ideals

@@

@@

\item Accelerate GB reduction
	\item $F_4$ algorithm on term-sparse polynomial ideal (parallel computing)
	\item ZDDs can represent chain of OR gates logic in linear space complexity (alternative canonical graphic representation)
\item Compute Craig's interpolants using algebraic geometry
	\item Projection of varieties $\implies$ interpolants

@@

\begin{frame}{\large{Future work: Craig's interpolants}}
\includegraphics[scale=0.3]{venn_craig.pdf}

@@

\item $ A \wedge B = \emptyset$, $A = (\overline{d})(\overline{c})(\overline{a}\vee
d)$ and  $B = (a \vee b \vee c)(\overline{b})$
\item $P = \overline{a}\wedge \overline{c}$ is an interpolant of $(A, B)$
\item Find interpolant from resolution tree [K. Mcmillan '03]
\item Algebraic geometry: projection in affine space
